Species-specific effects of the Urban Heat Island on tree growth across Berlin

### 2020-10-22 analysis/paper/paper.Rmd
stopped using package format explored LCZ from WUDAPT
re-ran analyses

if (grepl("docx", out_format) ||
    knitr::is_latex_output() ) {
  table_dat_req <- dat_req %>% 
  select(-owned) %>% 
  knitr::kable(booktabs = TRUE,

@@

} else {
  table_dat_req <- dat_req %>% 
  select(-owned) %>% 
  knitr::kable(booktabs = TRUE,
               format = "html",
               caption = "Data requirements for analysis, including currently available/accessed and required/desired data.",
             caption.short = "Data requirements for analysis",
             col.names = c("Subject/Relevance",
                          "Desc.",
                          "Type",
                          "Obsv. (n)",
                          "Resolution (m)",
                          "Source")) %>% 
  kableExtra::kable_styling(full_width = TRUE, 
                            font_size = 10) %>% 
  kableExtra::row_spec(0, bold = TRUE) %>% 
  kableExtra::pack_rows("available or accessed", 1, 4) %>%
  kableExtra::pack_rows("required and/or desired", 5, 9)

>>>>

if (grepl("docx", out_format) ||
    knitr::is_latex_output() ) {
  table_dat_req <- dat_req %>% 
  dplyr::select(-owned) %>% 
  knitr::kable(booktabs = TRUE,

@@

} else {
  table_dat_req <- dat_req %>% 
  dplyr::select(-owned) %>% 
  knitr::kable(booktabs = TRUE,
               format = "html",
               caption = "Data requirements for analysis, including currently available/accessed and required/desired data.",
             caption.short = "Data requirements for analysis",
             col.names = c("Subject/Relevance",
                          "Desc.",
                          "Type",
                          "Obsv. (n)",
                          "Resolution (m)",
                          "Source")) %>% 
  kableExtra::kable_styling(full_width = TRUE, 
                            font_size = 10) %>% 
  kableExtra::row_spec(0, bold = TRUE) %>% 
  kableExtra::pack_rows("available or accessed", 1, 4) %>%
  kableExtra::pack_rows("required and/or desired", 5, 9)
